Estimating individual subjective values of emotion regulation strategies

### 2023-02-13 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
added package name

library(papaja) # APA conform output
library(kableExtra) # for tables in R Markdown
library(BayesFactor) # for bayes factors

@@

@@

`r afex::nice(SubjArousalView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjArousalView_pilot_BF)$bf, digits = 2)`

@@

ANOVA: `r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`

@@

*Corrugator*: ANOVA: `r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`

@@

*Levator*: ANOVA: `r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`

@@

*Corrugator*: ANOVA: `r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`

@@

*Levator*: ANOVA: `r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`

@@

ANOVA: `r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`

>>>>

library(papaja) # APA conform output
library(kableExtra) # for tables in R Markdown
#library(BayesFactor) # for bayes factors

@@

```{r child = "Results.Rmd"}
```

@@

`r afex::nice(SubjArousalView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(SubjArousalView_pilot_BF)$bf, digits = 2)`

@@

ANOVA: `r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`

@@

*Corrugator*: ANOVA: `r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`

@@

*Levator*: ANOVA: `r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`

@@

*Corrugator*: ANOVA: `r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`

@@

*Levator*: ANOVA: `r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`

@@

ANOVA: `r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`
